Algebraic Tori in Unitary Groups

### 2014-10-08 Paper.tex
Add a couple more TODOs

@@

>>>>

\TODO{We should have a corrallary to make the above remark specific}
\TODO{Rational conjugacy classes <-> involutions up to rational conjugacy <-> $E^\sigma/N(E)$}

@@

\TODO{We still never actually prove that rational conjugacy is equivalent to choice of $\lambda$}
\TODO{We should say something back at the end of 4.1 about this}
\TODO{In this section we just need to say which $\lambda\in E^{\sigma}/N_{E/E^\sigma}(E)$ actually give each isomorphism class and which isomorphism classes are possible}
